\section{Experiments}
\label{sec:experiments}


\subsection{Experimental Setup}
\label{sec:setup}

\subsubsection{Datasets}
\label{sec:datasets}

\paragraph{DiDi GAIA Dataset (Chengdu, China).}
\label{sec:dataset_didi}
We evaluate on the \textit{DiDi GAIA Open Dataset}, a publicly available corpus
of high-resolution GPS trajectories and trip dispatch logs collected from
ride-hailing operations in Chengdu, China. The full corpus covers 30 days in
November 2016, comprising approximately 7.06 million completed trips and over
1.09 billion GPS pings. To measure strategy performance under a realistic but
reproducible demand profile, we designate a single held-out test day
(9 November 2016, a representative weekday) as our primary evaluation
instance, comprising 36,799 workers and 224,219 tasks.

We focus on the core urban area centred at approximately $30.67^\circ$N,
$104.07^\circ$E. All distance computations use a flat-earth (equirectangular)
projection calibrated to the mean latitude of all simulation participants,
converting geographic coordinates to kilometres with a worst-case
approximation error below 0.15\% over the city extent. Travel times assume a
constant average urban speed of 30\,km/h with Manhattan-distance routing.

\textit{Entity modelling.}
Simulation entities are derived from the raw logs as follows.

\begin{itemize}
    \item \textbf{Workers.} Each unique driver identifier active on the test
    day yields one worker. The worker's spawn location and online time are
    taken from their first recorded GPS ping. A nominal shift duration of
    8 hours is applied; workers are removed from the candidate pool once they
    can no longer complete a trip before their shift deadline.

    \item \textbf{Tasks.} Each trip record is converted into one matching
    request. The original dispatch timestamp serves as the task release time
    $r_j$, and the billing-completion timestamp serves as the expiry deadline
    $e_j$. Task revenue is taken from the actual trip fare recorded in the
    billing log, providing a realistic revenue signal for platform-utility
    evaluation.
\end{itemize}

\paragraph{Gowalla LBSN Dataset (Austin, Texas).}
\label{sec:dataset_gowalla}
To assess the generalisability of our strategies beyond the ride-hailing
domain, we incorporate the \textit{Gowalla} location-based social network
(LBSN) check-in dataset~\cite{cho2011friendship}, made publicly available via
the Stanford SNAP repository. Gowalla records voluntary user check-ins at
named venues, providing a geographically diverse, community-sourced
alternative to operator-logged ride-hailing data. We use this dataset to
evaluate whether strategy rankings observed on DiDi hold under a
fundamentally different platform type, geographic region, and participant
behaviour model — with all strategy hyperparameters held fixed at their
DiDi-tuned values.

\textit{Regional realisation.}
We restrict our analysis to the Austin, Texas cluster
(29.9°–30.7°N, 97.5°–98.1°W), the densest Gowalla check-in cluster in the
continental United States, providing the highest concurrent task density
available in the dataset. We further restrict to September 2010 (29 days),
explicitly excluding March 2010, which is inflated by South by Southwest
(SXSW) festival activity and would introduce an unrepresentative spatial
concentration.

\textit{Temporal compression.}
Raw LBSN check-in arrival rates are approximately 150$\times$ lower than
ride-hailing trip rates. Without preprocessing, the September 2010 Austin
corpus yields only $\sim$31 tasks active simultaneously across the 29-day
horizon — a density too sparse for strategies to differentiate. To recover a
city-scale simulation environment while preserving the authentic intra-day
demand rhythm, we apply \textit{temporal compression}: the calendar date is
stripped from every check-in, retaining only the wall-clock time (HH:MM:SS),
and all events are projected onto a single 24-hour reference window. This
stacks 29 days of check-ins into one simulated day, increasing concurrent
task density from $\sim$31 to $\sim$910 — comparable to the DiDi environment —
without altering spatial distributions or relative intra-day ordering.

\textit{Entity modelling.}
Simulation entities are derived from the compressed check-in log as follows.

\begin{itemize}
    \item \textbf{Workers.} Each unique (user\_id, calendar\_day) pair
    yields one worker, with spawn location and online time taken from that
    user's first check-in on that day. Worker deduplication is performed on
    the original calendar dates (prior to compression) to preserve the full
    pool of 8,758 unique worker-days; using post-compression dates would
    collapse all days to a single reference date and reduce the pool to
    $\sim$2,600 unique users. A shift duration of 8 hours is applied, and
    workers are downsampled to a worker-to-task ratio of 1:5 (random seed 42)
    to match the supply-demand regime observed in the DiDi dataset.

    \item \textbf{Tasks.} Each individual check-in is converted into one
    matching request, with the check-in location as the pickup point and a
    30-minute expiry window ($e_j = r_j + 1800$\,s). As LBSN data records
    only the arrival venue and not a subsequent destination, dropoff
    locations are generated synthetically by displacing the pickup point by
    Gaussian noise with $\sigma = 2$\,km (converted to degrees using the
    local great-circle approximation). Revenue is computed as a
    distance-proportional proxy based on the Euclidean pickup-to-dropoff
    distance.
\end{itemize}

After compression and downsampling, the Gowalla evaluation instance
comprises 8,758 workers and 43,788 tasks.

\subsubsection{Implementation Details}
\label{sec:framework}

\textbf{Discrete event simulation.}
We implement a discrete event simulator (DES) driven by a min-heap priority
queue ordered on Unix timestamps, ensuring that strategy decisions are
processed in strict chronological order with no artificial batching or
lookahead. This adheres to the \textit{instantaneous matching constraint} of
online spatial crowdsourcing~\cite{tong2019survey}: each assignment decision
must be made the moment a participant arrives, without knowledge of future
events. Four event types are supported:

\begin{itemize}
    \item \textsc{WorkerRelease} — a worker comes online and immediately
    triggers the \textsc{FreeWorker} handler to scan for pending tasks.
    \item \textsc{TaskRelease} — a task enters the pending pool and
    immediately triggers the \textsc{NewTask} handler to scan for available
    workers.
    \item \textsc{TaskComplete} — a worker finishes a trip, returns to the
    candidate pool, and triggers a second \textsc{FreeWorker} call to claim
    the next pending task.
    \item \textsc{TaskExpire} — an unassigned task whose deadline $e_j$ has
    elapsed is purged from the pending pool, preventing infeasible
    assignments.
\end{itemize}

Each strategy is implemented as a pair of handlers
$(\textsc{NewTask}, \textsc{FreeWorker})$ that receive the current system
state and return zero or one assignments. The simulator is dataset-agnostic:
the same engine processes both the DiDi and Gowalla instances without
modification.

\textbf{Spatial index.}
Available workers are maintained in a $k$-d tree spatial index keyed on
their current position. This enables O($k\log n$) $k$-nearest-neighbour
queries, which underpin the O($k$) complexity of our proposed strategies.
The index is updated incrementally as workers transition between available
and busy states, avoiding full rebuilds on each event.

\textbf{Distance model and feasibility.}
All distances are computed using Manhattan distance under a flat-earth
equirectangular projection calibrated to the mean latitude of all simulation
participants, with worst-case coordinate error below 0.15\% over the city
extent. Travel times assume a constant average urban speed of 30\,km/h.
Every candidate assignment is gated by a dual feasibility check: (i) the
worker must reach the pickup point before the task deadline,
$t_{\text{now}} + d_{\text{pick}}/v \leq e_j$; and (ii) the worker must
reach the dropoff destination before their shift deadline,
$t_{\text{now}} + (d_{\text{pick}} + d_{\text{drop}})/v \leq
t_{\text{deadline}}^w$. Assignments failing either condition are silently
rejected, preventing constraint violations without requiring explicit
penalty terms.

\subsubsection{Baselines}
We benchmark our approach against the following existing task assignment
approaches in the literature.

\begin{itemize}
    \item \textbf{Greedy:} Minimizes pickup distance only
    ($\lambda_1, \lambda_2 = 0$).

    \item \textbf{Least Allocated Worker First (LAF):} Pure fairness
    baseline that assigns tasks to workers with the fewest completed tasks.

    \item \textbf{EWMA-Only:} A fairness-only baseline that prioritises
    worker assignment using an exponentially weighted moving average (EWMA)
    of idle time, following the same fairness signal as our composite
    framework but without utility or starvation components.

    \item \textbf{BiRanking (BRK):} A randomised baseline inspired
    by \cite{[CITATION]} that assigns permanent random ranks to workers and
    tasks at arrival time, then greedily matches the lowest-ranked feasible
    pair at each event.

    \item \textbf{FATP-ANN:} A fairness-aware baseline from existing
    work \cite{CR-08}.

    \item \textbf{Fixed-Composite:} A static weight configuration of the
    proposed composite assignment framework, tuned via grid search on the
    training set.

    \item \textbf{TSGF Sampling:} A randomised policy-sampling baseline
    adapted from the Two-Sided Group Fairness framework \cite{[CITATION]},
    which samples one of three sub-heuristics — operator profit, worker
    fairness, or task fairness — at each dispatch event with probabilities
    $\alpha$, $\beta$, $\gamma$ respectively.

    \item \textbf{Cost-Balancing (CB):} An online batching
    baseline \cite{[CITATION]} that defers assignment until the estimated
    matching cost is bounded by a factor $\alpha$ of the accumulated
    waiting cost, then runs a greedy batch match.

    \item \textbf{Discrete Review LP:} A fixed-interval batch-matching
    baseline from \cite{[CITATION]} that defers all arrivals and solves a
    global bipartite assignment problem via the Hungarian algorithm at
    periodic review epochs, maximising spatial utility subject to task
    expiry and worker deadline constraints.

    \item \textbf{ONRTA-RT:} The randomised-threshold variant of the
    Online Non-Rejection Task Assignment policy \cite{[CITATION]}, which
    draws a random utility threshold $\theta$ at the start of each episode
    and accepts only worker–task pairs whose utility exceeds $\theta$.

    \item \textbf{ONRTA-OP:} The optimal-threshold variant
    of \cite{[CITATION]}, a two-stage policy that applies a greedy
    heuristic in the first half of the horizon and switches to a globally
    optimal bipartite matching in the second half, using expected arrival
    counts to set the stage transition point.

    \item \textbf{MMD-Batch (MMD-BB):} A batch-based heuristic
    baseline from \cite{CR-11} that periodically buffers tasks and
    available workers to minimise the bottleneck (maximum) delay, defined
    as the summation of task buffering time and worker travel time. This
    approach utilises a periodic bipartite matching process to optimise
    worst-case individual performance rather than global average utility.
\end{itemize}

\subsubsection{Evaluation Metrics}
To evaluate the effectiveness of the proposed composite assignment framework
in navigating the tripartite trade-off between efficiency, fairness, and
starvation prevention, we report the following metrics across all strategies.

\textbf{1) Platform Economics \& Efficiency:}
We use the \textit{Task Assignment Ratio} (TAR) as the primary indicator of
system throughput, defined as the fraction of successfully matched requests
relative to total task arrivals ($|M| / |\mathcal{T}|$). We additionally
report \textit{Total Platform Revenue} (k\$) to capture economic viability,
as higher-revenue trips contribute disproportionately to overall platform
sustainability.

\textbf{2) Supply-Side Equity:}
We measure distributive fairness using \textbf{Jain's Fairness Index (JFI)}
\cite{JFI-Original} computed over the vector of cumulative task counts
$\mathbf{x}$ across all active workers:
\begin{equation}
    JFI(\mathbf{x}) = \frac{(\sum_{i=1}^{n} x_i)^2}{n \sum_{i=1}^{n} x_i^2}
\end{equation}
where $n$ is the number of workers. A JFI approaching 1.0 indicates that
tasks are distributed equitably across the workforce.

\textbf{3) Demand-Side Reliability:}
We quantify customer-facing service quality through two complementary
metrics. \textit{Mean Wait Time} (minutes) measures the average interval
from task release $r_j$ to worker pickup, capturing overall responsiveness
of the assignment policy. \textit{Average Pickup Distance} (km) measures
the mean empty distance a worker travels to reach the pickup origin,
serving as a direct proxy for the spatial cost of each dispatch decision.
Together, these metrics reveal whether a strategy achieves low wait times
through genuinely efficient spatial matching or by accepting long,
costly detours to serve requests quickly.

\textbf{4) Starvation \& Operational Overhead:}
We report \textit{Peak Backlog} — the maximum number of simultaneously
unassigned tasks observed during a simulation day — as a measure of
the system's resilience to demand spikes. A backlog of zero indicates that
the strategy drains the active task pool without accumulation. Finally, we
include \textit{Wall-clock Runtime} (seconds) to assess the practical
computational cost of each strategy, as tractability at city-scale is a
prerequisite for real-world deployment.

\subsection{Effectiveness}
\label{sec:overall_results}
\begin{table}[h]
\caption{Strategy Performance on a Representative Held-out Test Day (9 November 2016, Chengdu DiDi GAIA Dataset). $\dagger$ denotes our proposed method. Bold values indicate the best performance in each metric. $^*$Values pending confirmation from full benchmark run.}
\label{tab:main_results}
\centering
\small
\begin{tabularx}{\columnwidth}{|X|c|c|c|c|c|c|}
\hline
\textbf{Strategy} & \textbf{Rev. (k\$)} $\uparrow$ & \textbf{Wait} $\downarrow$ & \textbf{JFI} $\uparrow$ & \textbf{TAR} $\uparrow$ & \textbf{Backlog} $\downarrow$ & \textbf{Time (s)} $\downarrow$ \\ \hline
Greedy                       & 2,765          & 2.614          & 0.594          & \textbf{0.863} & 140            & 341.7          \\ \hline
EWMA-Only$^{\ddagger}$       & ---            & ---            & ---            & ---            & ---            & ---            \\ \hline
LAF \cite{CR-10}             & 2,765          & 9.643          & \textbf{0.705} & \textbf{0.863} & 155            & 268.1          \\ \hline
BiRanking (BRK)              & 2,751          & 12.344         & 0.592          & 0.857          & \textbf{0}     & 381.6          \\ \hline
FATP-ANN \cite{CR-08}        & 2,752          & 3.402          & 0.557          & 0.853          & 693            & 1,714.8        \\ \hline
ONRTA-RT                     & 2,750          & 12.172         & 0.642          & 0.855          & \textbf{0}     & 338.5          \\ \hline
ONRTA-OP                     & 2,765          & 2.623          & 0.594          & \textbf{0.863} & \textbf{0}     & 488.5          \\ \hline
Disc. Review LP              & 2,764          & \textbf{1.916} & 1.000          & 0.862          & \textbf{0}     & 3,248.1        \\ \hline
k-NLF ($k{=}15$)$^\dagger$   & $\approx$2,766$^*$ & 3.476      & 0.645          & \textbf{0.863} & $^*$           & \textbf{37.5}  \\ \hline
\textbf{Composite}$^\dagger$ & \textbf{2,767} & 3.286          & 0.584          & \textbf{0.863} & \textbf{0}     & 103.6          \\ \hline
\end{tabularx}
\end{table}



\subsection{Efficiency & Scalability}

\subsection{Ablation & Sensitivity Analysis}
\subsubsection{Impact of k}
\subsubsection{Task-Count vs EWMA}
\subsubsection{Weighted Scorer Sensitvity}